Allocation Removal by Partial Evaluation in a Tracing JIT

### 2011-01-11 talk/pepm2011/presentation/talk.tex
fix conclusion

\begin{frame}
  \frametitle{Conclusion}
  \begin{itemize}
      \item very simple partial-evaluation-based
      \item successful application of partial evaluation
      \item Prolog can benefit from dynamic compilation
  \end{itemize}
  \pause
  \begin{block}{Future}
      \begin{itemize}
          \item Scale up to larger programs
          \item need some optimization on the interpreter level – indexing
          \item investigate memory usage
      \end{itemize}
  \end{block}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Conclusion}
  \begin{itemize}
      \item very simple partial-evaluation-based optimization
      \item can remove a lot of allocations and type checks in practical programs
      \item no control issues
      \item all control decisions made by the tracer
      \item based on observing executing program
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Questions?}
  \begin{itemize}
      \item very simple partial-evaluation-based optimization for tracing JITs of dynamic languages
      \item can remove a lot of allocations and type checks in practical programs
      \item no control issues
      \item all control decisions made by the tracing JIT
      \item based on observing executing program
  \end{itemize}
\end{frame}
